Another paper with lots of text and fancy pictures

### 2023-11-27 paper.tex
Make plots bigger

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\linewidth]{images/carb.npy-surf3.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/carb.npy-surf2void.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/carb.npy-surfvoid2.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{images/carb.npy-s3.png}
  \includegraphics[width=0.3\linewidth]{images/carb.npy-c3.png}
  \caption[]{Correlation functions for carbonate sample
    (\cref{fig:sample-limestone}).}
  \label{fig:sample-limestone-cf}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.45\linewidth]{images/carb.npy-surf3.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/carb.npy-surf2void.png}
  \vskip\baselineskip
  \includegraphics[width=0.45\linewidth]{images/carb.npy-surfvoid2.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/carb.npy-s3.png}
  \vskip\baselineskip
  \includegraphics[width=0.45\linewidth]{images/carb.npy-c3.png}
  \caption[]{Correlation functions for carbonate sample
    (\cref{fig:sample-limestone}).}
  \label{fig:sample-limestone-cf}
\end{figure}
